---
title: "Populating Imports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Populating Imports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sinew)
```

When you are building a package to submit to CRAN and you need to have namespace calls for any function that is being imported. It is a pain to manually parse through the code looking for all the *::* and writing it in the [roxygen2](https://cran.r-project.org/web/packages/roxygen2/vignettes/roxygen2.html) header. This function does that for you.

You can write normally your script with the __namespace__ calls and in the end run the function and you can paste the output into the header. (or use it as part of `sinew::makeOxygen` or `sinew::makeOxyFile`)

The function is written to work on single files or whole directories, like a package `R` subdirectory.

The output can be set to return the format needed for either an [roxygen2](https://cran.r-project.org/web/packages/roxygen2/vignettes/roxygen2.html) header or the `DESCRIPTION`

## Package Setup

```{r,results='hide'}
pkg_dir <- file.path(tempdir(),'pkg')
pkg_dir_r <- file.path(pkg_dir, 'R')

usethis::create_package(path = pkg_dir, open = FALSE)
withr::with_dir(pkg_dir, usethis::use_data_raw(open = FALSE))
withr::with_dir(pkg_dir, usethis::use_mit_license(name = "John Doe"))
withr::with_dir(pkg_dir, usethis::use_roxygen_md())

```
 
```{r}
example_file <- system.file('example.R', package = 'sinew')

```
 
```{r}
untangle(
  file = example_file, 
  dir.out = pkg_dir_r, 
  dir.body = file.path(pkg_dir, 'data-raw')
)

```
 
```{r,results='hide'}
pretty_namespace(pkg_dir_r,overwrite = TRUE)
```

## DESCRIPTION

```{r}
make_import(script = pkg_dir_r,format = 'description')
```

To write the output directly into the Imports field of the `DESCRIPTION` file, specify path to `DESCRIPTION` in `desc_loc`

```{r}
sinew::update_desc(path = pkg_dir_r, overwrite = TRUE)
```

```{r, echo = FALSE}
details::details(file.path(pkg_dir,'DESCRIPTION'), summary = 'Click to see DESCRIPTION file',lang = '')
```

## roxygen2

```{r}
#single file
make_import(script = file.path(pkg_dir_r,'yy.R') ,format = 'oxygen')
```

```{r}
#whole directory
make_import(script = pkg_dir_r,format = 'oxygen')
```

## Cutoff

Setting the parameter `cut` to an integer value allows for control of how many functions to list in a package before concatenating the `importFrom` to an import. This is useful when there are many functions being used throughout the package from the same library and it is practically the same as just importing the whole library

```{r}
#with cut
make_import(script=file.path(pkg_dir_r,'yy.R'),format = 'oxygen', cut = 1)
```

### Cleanup

```{r}
unlink(pkg_dir, recursive = TRUE, force = TRUE)
```
