---
title: "Session Options"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Session Options}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sinew)
```

`sinew` options can be set to remain persistent across sessions or at a global level within a session

For those familiar with `knitr` `sinew` follows the same option logic, and instead of `knitr::opts_chunk` we define `sinew::sinew_opts`.

The defaults settings for the core function parameters in `sinew` are defined in `sinew_opts`. These include the [roxygen2](https://cran.r-project.org/web/packages/roxygen2/vignettes/roxygen2.html) fields and their values to include by default in the function header.

These settings will persist for a `R` session.

If the user needs the settings to persist across sessions, like in package development, sinew reads on load a file called `_sinewconfig.yml`, placed in the working directory.

## Using _sinewconfig.yml

When loading the `sinew` package the file `_sinewconfig.yml` will be searched for in the working directory, if found settings found in it will be used instead of the package defaults.

To create the `_sinewconfig.yml` file in the current project directory and update the `.Rbuildignore` automatically use the function `create_yml()`.
In the example below the field author will be added to all [roxygen2](https://cran.r-project.org/web/packages/roxygen2/vignettes/roxygen2.html) headers returned by `sinew` and its value is `Jonathan Sidi`.

```yml
add_fields: ["author"]
author: 'Jonathan Sidi'
```

## Using sinew_opts

Retrieve all current values

```{r}
sinew_opts$get()
```

Retrieve a specific field

```{r}
sinew_opts$get('author')
```

Retrieve a multiple fields

```{r}
sinew_opts$get(c('author','source'))
```

Set a value

```{r}
sinew_opts$set(list(author='John Doe'))
sinew_opts$get('author')
```

Append a new value to the current field values

```{r}
sinew_opts$get('add_fields')
```

```{r}
sinew_opts$append(add_fields='source')
sinew_opts$get('add_fields')
```

Reset fields to package defaults

```{r}
sinew_opts$restore()
sinew_opts$get(c('add_fields','author'))
```
